Agents and you, a brief summary

### 2015-10-29 agents/summery.tex
added some markov things
added the probability craP??

\section{Markov}

\subsection{Exam}

>>>>

\section{Markov}
Computerised decision makers must deal with an uncertain world.

\subsection{Expectation}
Excpectation is the average value you excpect to happen. For example if you
throw a dice the average value you should get is 3.5. Because:

\[1 * 1/6 + 2 * 1/6 + 3 * 1/6 + 4 * 1/6 + 5 * 1/6 + 6 * 1/6 = 3.5\]

You multiple all possible values time the chance of them happening and then
calculate the sum of them. Formally it is written like this:

\[ E[X]=Def \sum_{all x} xP\{X=x\} \]

So you can fill it in like:
\[E[X]= 1 * P\{X=1\} + \cdots + 6 *P\{X=6\}\]
\[E[X]= 1 * 1/6 + \cdots + 6 *1/6 = 3.5\]

\subsubsection{Properties of expectation}

\begin{itemize}
	\item $E[c] = c$
	\item $E[X+Y] = E[X] + E[Y]$
	\item $E[cX] = cE[X]$
	\item $E[XY] = E[X]E[Y]$ if and only if $X$ and $Y$ are independent.
	\item $E[X] \le E[Y]$, if $X \le Y$ almost surely.
\end{itemize}

\paragraph{Law of the onconcious statistician}
You have to prove this, its \emph{not} a property:

\[E[g(X)]=\sum_{all x} g(x)P{X=x}\]

where $g$ is any real-valued function. (It returns a value that is part
of the real set of numbers).

\subsection{Conditional expectation}
The expectation of $X | Y = y$ is called the \emph{conditional expectation}
of $X$ given $Y$, and is denoted by:

\[E[X|Y=y]\]

$E[X|Y=y]$ Is a number that depends on $y \in Y$. So you only get an
expectation $X$ if you have an y that satisfies the condition.
This yields a random variable $E[X|Y]$. Because of this it has all the
properties of a random variable.

\subsubsection{Probability mass functions}
The standart notation for probability mass functions is:

\[p_x(x): D(X) \to [0,1]: x \mapsto P\{X=x\} \]
\[p_y(y): D(Y) \to [0,1]: y \mapsto P\{Y=y\} \]
\[p_{xy}(x,y): D(X) \times D(Y) \to [0,1]: (x,y) \mapsto P\{X=x,Y=y\} \]
\[p_{x|y}(x|y): D(X) \times D(Y) \to [0,1]: (x,y) \mapsto P\{X=x|Y=y\} \]

For example:

\[ P\{X=x|Y=y\}=\frac{P\{X=x,Y=y\}}{P\{Y=y\}}\]

Is often written as:

\[P_{x|y}(x|y)=\frac{P_{xy}(x,y)}{P_y(y)}\]

\subsection{Exam}
 For a given decision problem with a certain
discount factor.A pure policy sufices.
Do policy iteration, (a single iteration), do value iteration
(single iteration).
